Relative Photometry of HD 227858 and HD 338931 from Landholt Standard SA 113475

### 2013-12-10 paper.tex
getting somewhere

From \ref{eq:ext} and reference data for SA 113475, we arrive at the extinction coefficients:
\begin{align*}
k_B&= 0.583\\
k_V&= 0.176\\
k_R&= 0.131\\
k_I&= 0.166
\end{align*}
\begin{equation}
\label{eq:ext}
m_1-m_2=k(X_1-X_2)=-2.5\log_{10}\frac{S_1t_2}{S_2t_1}
\end{equation}
\section{Analysis}
$S_{*,sky}=\Delta\nu{\obar{\Phi}}{\obar{f}}tA/g$

>>>>

From Equation \ref{eq:ext} and reference data for SA 113475, we arrive at the extinction coefficients:
\begin{align*}
k_B&= 0.583\\
k_V&= 0.176\\
k_R&= 0.131\\
k_I&= 0.166
\end{align*}
\begin{equation}
\label{eq:ext}
m_a-m_a'=k(X_a-X_a')=-2.5\log_{10}\frac{S_at_a'}{S_a't_a}
\end{equation}

With known magnitudes of a calibration star, we can use Equation \ref{eq:targetstar} to determine the magnitude of
the target star, $m_*$.
\begin{equation}
\label{eq:targetstar}
m_{rel,*}=m_*-m_r=k(X_r-X_*)-2.5\log_{10}\frac{S_*t_r}{S_rt_*}
\end{equation}
So relative to SA 113475, the target stars have relative magnitudes: FIXME add in intrinsic - it's ok
\begin{center}
\begin{tabular}{c | c | c }
Star & Filter & $m_{rel,*}$\\
\hline
HD 227858 & B & -0.067 \\
HD 227858 & V & +0.165 \\
HD 227858 & R & +0.317  \\
HD 227858 & I &   -0.585 \\

HD 338931 & B & -1.596 \\
HD 338931 & V & -1.295 \\
HD 338931 & R &  -1.160\\
HD 338931 & I & -2.190 \\
\end{tabular}
\end{center}

k tells us what the observed magnitude (m_obs = kX + m_int)

\section{Analysis}
$S_{*,sky}=\Delta\nu{\obar{\Phi}}{\obar{f}}tA/g$

FIXME
We can determine the precise relationship between flux and signal for each filter as well, using Equation \ref{eq:convert}
\begin{equation}
S_{*,sky}=\frac{\Delta\nu \obar{\Phi}t\obar{f}A}{g}
\label{eq:convert}
\end{equation}
where $\obar{f}$ is the averaged flux in the filter band, $t$ is the exposure time, $A$ is the aperture of the telescope (area at entry),
$g$ is the gain in electrons per count, $\obar{\Phi}=\obar{ql\phi}$ is the averaged response of the system over the filter, and $\Delta\nu$ is the
bandwidth of the filter.
